Understanding Expectation Formation from Probabilistic Surveys

### 2019-06-17 slides/ExpSlides.tex
lstarted working on individual moments

\begin{frame}{Identified Inflation shocks}

@@

\begin{frame}{Inflation IR to  shocks}

@@

\begin{frame}{Inflation IR to  shocks}

@@

\subsection{Professional forecasters as a baseline }

\begin{frame}{Forecasting errors IR to  shocks}

@@

\begin{frame}{Disagreements IR to  shocks}

@@

\begin{frame}{Uncertainty IR to shocks}

>>>>

\begin{frame}{Inflation shocks}

@@

\begin{frame}{Inflation IR to  shocks exluding monetary policy}

\begin{figure}
	\includegraphics[scale=0.3]{figures/CPIAU_ashocks_nmp.png} 
\end{figure}

\begin{frame}{Inflation IR to  shocks including monetary policy}

@@

\begin{frame}{Inflation IR to  shocks excluding monetary policy}

\begin{figure}
	\includegraphics[scale=0.3]{figures/PCEPI_ashocks_nmp.png} 
\end{figure}

\begin{frame}{Inflation IR to  shocks including monetary policy}

@@

\subsection{Benchmark Results from Professional Forecasters }

\begin{frame}{Forecasting errors IR to  shocks excluding monetary policy}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFFE_ashocks_nmp.png} 
\end{figure}

\begin{frame}{Forecasting errors IR to  shocks including monetary policy}

@@

\begin{frame}{Disagreements IR to  shocks excluding monetary policy}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFDisg_ashocks_nmp.png} 
\end{figure}

\begin{frame}{Disagreements IR to  shocks including monetary policy}

@@

\begin{frame}{Uncertainty IR to shocks excluding monetary policy}

\begin{figure}
	\includegraphics[scale=0.3]{figures/SPFVar_ashocks_nmp.png} 
\end{figure}

\begin{frame}{Uncertainty IR to shocks including monetary policy}
